The \project{unRAVE} catalog

### 2016-09-07 article/unrave.tex
To satisfy @dfm
de-stub

\newcommand{\difftoday}[3]{%
  \setmydatenumber{dateone}{\the\year}{\the\month}{\the\day}%
  \setmydatenumber{datetwo}{#1}{#2}{#3}%
  \addtocounter{datetwo}{-\thedateone}%
  \the\numexpr(\thedatetwo)\relax\space days
}
% ------------------------------------------

@@

\begin{document}
% Remove at submission:
\slugcomment{{\color{red} \textbf{To appear on arXiv on 13 September 2016 (\difftoday{2016}{9}{9}away)}}}

@@

If the metallicities of metal-poor giant stars are on the same scale as the \apogee\
abundances, there is a larger issue in verifying that the main-sequence metallicities
and giant branch metallicities are on the same scale.  The training set for the
main-sequence stars includes metallicities from a variety of sources --- including
\lamost, and the fourth \rave\ data release.  Even on expectation value, there is 
no straightforward manner to ensure that these two models produce metallicities on
the same scale.  We see no systematic offset in metallicities of dwarf and giant
stars that overlap between \rave\ and the \ges\ survey, and our examination of
globular and open clusters suggests that \stub{if there is a systematic offset, it must
be small.} Nevertheless, these are only verification checks based on $<1$\% of the
data, and there is currently insufficient data for us to prove both models are on
the same abundance scale.

>>>>

\newcommand{\difftoday}[3]{%
  \setmydatenumber{dateone}{\the\year}{\the\month}{\the\day}%
  \setmydatenumber{datetwo}{#1}{#2}{#3}%
  \addtocounter{datetwo}{-\thedateone}%
  \the\numexpr(\thedatetwo)\relax\space days}
% ------------------------------------------

@@

\begin{document}
% Remove at submission:
\slugcomment{{\color{red} \textbf{To appear on arXiv on 13 Sep 2016 (submission in \difftoday{2016}{9}{9})}}}

@@

If the metallicities of metal-poor giant stars are on the same scale as the \apogee\
abundances, there is a larger issue in verifying that the main-sequence metallicities
and giant branch metallicities are on the same scale.  The training set for the
main-sequence stars includes metallicities from a variety of sources --- including
\lamost, and the fourth \rave\ data release.  Even on expectation value, there is 
no straightforward manner to ensure that these two models produce metallicities on
the same scale.  We see no systematic offset in metallicities of dwarf and giant
stars that overlap between \rave\ and the \ges\ survey, suggesting that if there is
a systematic offset, it must be small. Nevertheless, these are only verification checks based on $<1$\% of the
data, and there is currently insufficient data for us to prove both models are on
the same abundance scale.
